Statistical Inference Course Assignment - Part 2 
========================================================

TNow in the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package. 
Load the ToothGrowth data and perform some basic exploratory data analyses 
Provide a basic summary of the data.
Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there's other approaches worth considering)
State your conclusions and the assumptions needed for your conclusions. 

```{r}
library(datasets)
library(ggplot2)
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
    geom_bar(stat="identity",) +
    facet_grid(. ~ supp) +
    xlab("Dose in mg") +
    ylab("Tooth length") +
    guides(fill=guide_legend(title="Supplement type"))
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
fit <- lm(len ~ dose + supp, data=ToothGrowth)
summary(fit)
confint(fit)
```

